Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-04-04 article.tex
Fix typo

Another challenge is the way models are defined.
Many tools support the \ac{SBML} \cite{huckaSBMLL3V2} as an exchange format,
a \emph{de facto} standard for \acp{CRN} that defines species, parameters and reactions between species.
As writing \ac{SBML} directly is impractical,
Tellurium uses a \ac{DSL} called Antimony \cite{smithAntimonyModularModel2009} for defining models.
\Acp{DSL} allows to reuse the same code in different programming environments,
but are not recognized by default in \acp{IDE}
and, therefore, they cannot provide syntax highlighting, code completion, refactoring, and static analysis.
For Antimony, an extension providing this capabilities was developed for Visual Studio Code,
but its maintenance could be a demanding task for the systems biology community.
In the case of PySB,
using Python's dynamic nature,
it developers designed a \ac{DSL} within Python.
To save keystrokes,
it uses the global scope to create species and parameters,
without explicitly assigning them to Python variables or to the model,
but this approach is not fully compatible with \acp{IDE},
affecting the development experience.

>>>>

Another challenge is the way models are defined.
Many tools support the \ac{SBML} \cite{huckaSBMLL3V2} as an exchange format,
a \emph{de facto} standard for \acp{CRN} that defines species, parameters and reactions between species.
As writing \ac{SBML} directly is impractical,
Tellurium uses a \ac{DSL} called Antimony \cite{smithAntimonyModularModel2009} for defining models.
\Acp{DSL} allows to reuse the same code in different programming environments,
but are not recognized by default in \acp{IDE}
and, therefore, they cannot provide syntax highlighting, code completion, refactoring, and static analysis.
For Antimony, an extension providing these capabilities was developed for Visual Studio Code,
but its maintenance could be a demanding task for the systems biology community.
In the case of PySB,
using Python's dynamic nature,
it developers designed a \ac{DSL} within Python.
To save keystrokes,
it uses the global scope to create species and parameters,
without explicitly assigning them to Python variables or to the model,
but this approach is not fully compatible with \acp{IDE},
affecting the development experience.
